\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species

### 2023-12-12 ms.Rnw
Update

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[authoryear,numbers]{natbib}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\tolerance=1000
\usepackage{url}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{hyphenat}
\usepackage{Sweave}
\bibliographystyle{apalike}
\newcommand{\blind}{0}

@@

\if1\blind
{
  \title{\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species}
\author{Bo Yang\\Department of Biostatistics, University of Michigan \And
        Jesse Wheeler\\Department of Statistics, University of Michigan \And
        Aaron A. King\\Department of Ecology and Evolutionary Biology \& \\ Center for the Study of Complex Systems, University of Michigan\\\And
        Edward L. Ionides\\Department of Statistics, University of Michigan}
  \maketitle
} \fi

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[authoryear,numbers]{natbib}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\tolerance=1000
\usepackage{url}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{hyphenat}
\usepackage{Sweave}
\bibliographystyle{apalike}
\newcommand{\blind}{1}

@@

\if1\blind
{
  \title{\bf Mechanistic models for panel data: analysis of ecological experiments with four interacting species}
\author{Bo Yang\\Department of Biostatistics, University of Michigan \\
        Jesse Wheeler\\Department of Statistics, University of Michigan \\
        Aaron A. King\\Department of Ecology and Evolutionary Biology \& \\ Center for the Study of Complex Systems, University of Michigan\\
        Edward L. Ionides\\Department of Statistics, University of Michigan}
  \maketitle
} \fi
